---
title: "Friday Code Challenge"
output: html_document
date: "2025-05-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Sliding Window Maximum

#### Problem:  

Given a numeric vector nums and an integer k, there is a sliding window of size k which is moving from the left of the array to the right. You can only see the k numbers in the window. Each time the sliding window moves right by one position.
Return a vector containing the maximum element in each sliding window.

#### Example:

Input:  
nums = c(1, 3, -1, -3, 5, 3, 6, 7)  
k = 3  

Output: 
c(3, 3, 5, 5, 6, 7)   

Explanation: 
Window position              Max
---------------                   -----
[1  3  -1] -3  5  3  6  7       3
 1 [3  -1  -3] 5  3  6  7       3
 1  3 [-1  -3  5] 3  6  7       5
 1  3  -1 [-3  5  3] 6  7       5
 1  3  -1  -3 [5  3  6] 7       6
 1  3  -1  -3  5 [3  6  7]      7
 
Constraints:
1 ≤ k ≤ length(nums)

``` {r}

window_max <- function(nums, window) {
  
  # calculate the remaining window beyond initial index
  rem_window <- window - 1
  
  # If the window is larger than total numbers
  # then just do max of nums
  if (length(nums) < window) {
    return(max(nums))
  } else {
    
    # set up empty vector
    x <- c()
    
    # iterate over nums based on window size
    # iterations calculated on total length of nums
    # less the window size plus 1 (starting point + remainder of window size)
    for (i in 1:(length(nums) - rem_window)) {
      x <- c(x, max(nums[i:(i + rem_window)]))
    }
  }
  
  return(x)
  
}

window_max(nums = c(1, 3, -1, -3, 5, 3, 6, 7), window = 3)

window_max(nums = c(5, -6, 1, 2, 8, -2, -4, -3, 10), window = 2)

window_max(nums = c(1, 5, -4, -3, 4, 12, 6, -1, 6, 7, 0), window = 5)

window_max(nums = c(1, 5), window = 5)


```



Angle between hour and minute hands
 
Problem:
  Write a function that determines the acute angle
  between hour and minute hands.
 

``` {r}

clock_angle <- function(hour, minute) {
  
  #minute degree movement
  minute_location <- minute * 6
  
  #hour degree movement
  hour_location <- hour %% 12 * 30 + minute * 1/2
  
  #still need to deal with going beyond 180
  hand_difference <- abs(hour_location - minute_location)
  
  # want acute angle 
  if (hand_difference > 180) hand_difference <- hand_difference - 180
  
  return(hand_difference)
  
}


clock_angle(hour = 12, minute = 30)
clock_angle(hour = 6, minute = 0)
clock_angle(hour = 3, minute = 30)
clock_angle(hour = 12, minute = 2)



```
