---
title: "Friday Code Challenge"
output: html_document
date: "2025-05-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Jump Game
 
Problem:
  You are given an integer vector nums.
  You are initially positioned at the vector's first index,
  and each element in the vector represents your maximum jump length
  at that position.
 
Return TRUE if you can reach the last index, or FALSE otherwise.
 
Example 1:
  Input: nums = [2,3,1,1,4]
  Output: TRUE
 
  Explanation:
    Jump 1 step from index 1 to 2, then 3 steps to the last index.
 
Example 2:
  Input: nums = [3,2,1,0,4]
  Output: FALSE
 
  Explanation:
    You will always arrive at index 4 no matter what.
    Its maximum jump length is 0, which makes it impossible to reach
    the last index.
 
Note:
  In R, index starts at 1.
 
 
``` {r}

jump <- function(nums) {
  
  # If no zeros we'll always get to the end
  if ( !0 %in% nums ) {
    return(TRUE)
  }
  
  # Find all 0's in the vector
  zero_index <- which(nums == 0)
  
  # Iterate the algorithm for each instance of 0 and see if we can jump
  # over it
  for (x in zero_index) {
    
    # If we only have one 0 and its at the end we'll always reach the end
    if ( length(zero_index) == 1 && x == length(nums) ) {
      return(TRUE)
      break
    } 
    
    # If the 0 is at the start we can't jump
    if ( x == 1 ) {
      return(FALSE)
      break
    } 
    
    # iterate over every index prior to 0 index and check
    # if their max jump will get past that index
    for ( i in 1:(x-1) ) {
      
      #browser()
      
      # Max jump distance for that index
      # we just need to find an index who's max jump is larger
      # than the distance between that index and the 0 index
      max_jump <- nums[i]
      
      # The distance between the current index
      # and the 0 index (ie. the minimum distance
      # that we'll need to jump over)
      jump_min <- (x - i)
      
      # If our jump is larger than the
      # distance then we'll make it over
      # if we make it then end the loop and finish
      # if we don't then next iteration
      if (max_jump > jump_min) {
        reach_end <- TRUE
        break
      } else {
        reach_end <- FALSE
        next
      }
    }
  }
  
  return(reach_end)
  
}


jump(c(3,2,0,1,4))
jump(c(1,1,2,0,4))
jump(c(1,1,2,0,4))
jump(c(3,2,1,1,4))
jump(c(3,1,0,1,4))
jump(c(1,1,0,1,4))
jump(c(1,1,1,1,0))
jump(c(2,2,0,0,2))
jump(c(2,0,1,0,2))
jump(c(2,0,3,0,2))
jump(c(0,0,3,0,2))
jump(c(0))

```

Given a biased coin (a function that toss a coin with bias), write a function to produce unbiased toss result.
 

``` {r}

#cheater
coin_tosser <- function(n, p) {
  
  x <- c()
  
  for (i in 1:n) {
    x[i] <- ifelse(sample(0:1, 1) == 1, "H", "T")
  }
  
  
}



#real

# essentially just use the TH or HT as a 50/50 odd and assign those as the results

bias_toss <- function(p_head) {
  sample(c('H', 'T'), prob = c(p_head, 1 - p_head), replace = T, size = 2)
}

assign_output <- function(p_head) {
  dbl_toss <- bias_toss(p_head)
  if (all(dbl_toss == c('H', 'T'))) return ('H')
  if (all(dbl_toss == c('T', 'H'))) return ('T')
  
  return(NULL)
  
}

unbiased_toss <- function(p_head, n = 1000) {
  
  tosses <- replicate(n = n, assign_output(p_head))
  
  tosses <- unlist(tosses)
  
  table(tosses)
  
  
}

get_toss_prob <- function(p_head, n = 1000) {
  tosses <- unbiased_toss(p_head, n)
  tosses['H'] / sum(tosses)
}

get_toss_prob(0.6)


```






