---
title: "Friday Code Challenge"
output: html_document
date: "2025-05-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 
Problem:
There are n light bulbs initially off. You toggle every i-th bulb in i-th round (i from 1 to n). After n rounds, which bulbs are on?
Explanation:
Microsoft has failed us with the lack of light bulb emojis so I will use  to represent off 

Say you have n = 5 light bulbs.

Round 0: all starts off


Round 1: "toggle every first light bulb in the first round" so that's all light bulbs


Round 2: "toggle every second light bulb in the second round" so that's every other light bulbs


Round 3: "toggle every third light bulb in the third round" so that's every third


Round 4: "toggle every fourth light bulb in the fourth round"


Round 5: "toggle every fifth light bulb in the fifth round"


Answer:

If n = 5, positions 1 and 4 bulbs are on.

 

``` {r}


light_switch_v1 <- function(n) {
  lights <- rep(F, n)
  message(paste0("Round 0:"))
  print(lights)
  for (i in 1:n) {
    for (x in seq_along(lights)) {
      #browser()
      if (x %% i == 0) {
        lights[x] <- ifelse(isTRUE(lights[x]), F, T) 
      }
    }  
    message(paste0("Round ", i, ":"))
    print(lights)
  }
}


light_switch_v2 <- function(n) {
  
  lights <- c()
  for (x in 1:n) {
    #browser()
    lights[x] <- ifelse(sum(x %% seq_along(1:n) == 0) %% 2 == 0, F, T) # 4 0s means flips 4 times
    
  }
  
  message(paste0("Round ", n, ":"))
  print(as.logical(lights))
  
}



light_switch_v3 <- function(n) {
  
  
  #only squares get flipped
  lights <- sqrt(1:n) %% 1 == 0
  
  message(paste0("Round ", n, ":"))
  print(as.logical(lights))
  
}

light_switch_v1(9)
light_switch_v2(9)
light_switch_v3(9)

```

#Give me the primes:
Prime numbers include 2, 3, 5, 7, and any other number that’s only divisible by itself and 1. Write a function in R that takes an integer as a parameter and returns all the prime numbers up to and including that integer.

``` {r}

n <- 7

primes <- function(n) {
  numbers <- 1:n
  for (i in numbers) {
    results[i] <- sum((i / seq_along(numbers)) %% 1 == 0) == 2
  }
  return(numbers[results])
}

primes(7)
primes(11)
primes(20)

