---
title: "Friday Code Challenge"
output: html_document
date: "2025-06-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 
Problem:
Suppose a vector of `n` integers representing "heights" of walls, and that each index is 1 unit apart from adjacent indices. Write a function to calculate the amount of water trapped between any two indices.

Explanation:
wall_heights <- c(1, 2, 4, 5, 3, 2, 1)

Visually:
         |
      |  |
      |  |  |  
   |  |  |  |  |
|<u>  </u>|<u>  </u>|<u>  </u>|<u>  </u>|<u>  </u>|<u>  </u>|
1  2  4  5  3  2  1
 ^  ^  ^  ^  ^  ^
These are the gaps where water can be trapped

Water between index 1 and 3: 3 units
         |
      |  |
    <u>  </u>|  |  |  
 <u>  </u>|  |  |  |  |
|<u>  </u>|<u>  </u>|<u>  </u>|<u>  </u>|<u>  </u>|<u>  </u>|
1  2  4  5  3  2  1
 
|x x x x| 
|x x x x|
|x|x|x|x|
 
``` {r}

water_units <- function(wall_heights, indices) {
   
   #reduce to just our indexed section
   section <- wall_heights[indices[1]:indices[2]]
   
   #remove one index of max value
   units <- sum(section[-which(section == max(section))[1]])
   
   return(units)
   
   }

water_units(c(1, 2, 4, 5, 3, 2, 1), c(1, 3))
water_units(c(1, 2, 4, 5, 3, 2, 1), c(2, 3))
water_units(c(1, 2, 4, 5, 3, 2, 1), c(1, 4))
water_units(c(1, 2, 4, 5, 3, 2, 1), c(1, 6))
water_units(c(1, 5, 5, 5, 3, 2, 1), c(1, 4))

water_units(c(5, 1, 1, 1, 1, 1, 5), c(2, 3))

```

#Give me the primes:
Prime numbers include 2, 3, 5, 7, and any other number that’s only divisible by itself and 1. Write a function in R that takes an integer as a parameter and returns all the prime numbers up to and including that integer.

Example:
n = 7
2, 3, 5, 7

``` {r}

n <- 7

primes <- function(n) {
   #create a vector of our numbers
  numbers <- 1:n
  results <- c()
  #go along the numbers
  for (i in numbers) {
     #browser()
     #we only want numbers that are divisible by itself and 1
     # that means we want to divide each number by every number 
     # in our vector, determine which ones have no remainder from 1, there
     # should be two in total - these are the primes
    results[i] <- sum((i / seq_along(numbers)) %% 1 == 0) == 2
  }
  return(numbers[results])
}

primes(7)
primes(11)
primes(20)


```