---
title: "Friday Code Challenge"
output: html_document
date: "2025-05-08"
---

# Problem:
# Print the Fibonacci series up to a given `limit`.
# Note: Start the series with 0, 1
# Example:
#   Input: limit = 10
#   Output: 0 1 1 2 3 5 8 13
#
#   Explanation: Add up two prior numbers to get next number. Continue until the recent value is greater than 10.
#
# Hint: While loop

``` {r}
# Define a function to print the Fibonacci series up to a given limit using a while loop
print_fibonacci_series <- function(limit) {
    # Initialize variables to store the first two numbers of the Fibonacci series
    a <- 0
    b <- 1
    
    # Print the first two numbers of the Fibonacci series
    cat(a, b, sep = " ")
    
    # Iterate while the next Fibonacci number is less than or equal to the limit
    while (b < limit) {
        # Calculate the next Fibonacci number
        next_num <- a + b
        
        # Print the next Fibonacci number
        cat(" ", next_num)
        
        # Update variables for the next iteration
        a <- b
        b <- next_num
    }
}

print_fibonacci_series(10)

#alternative where we don't go past the limit

print_fibonacci_series <- function(limit) {
  # Initialize variables to store the first two numbers of the Fibonacci series
  a <- 0
  b <- 1
  
  # Print the first two numbers of the Fibonacci series
  cat(a, sep = " ")
  
  # Iterate while the next Fibonacci number is less than or equal to the limit
  while (b <= limit) {
    # Calculate the next Fibonacci number
    next_num <- a + b
    
    # Print the next Fibonacci number
    cat(" ", b)
    
    # Update variables for the next iteration
    a <- b
    b <- next_num
  }
}

print_fibonacci_series(10)

```

# Problem:
# Calculate the `nth` term of the Fibonacci series using recursion.
# Note: The series starts with 0, 1.
# Example 1:
#   Input: `n = 0`
#   Output: 0
#
#   Explanation: Given the fibonacci sequence starts at n = 0, we reach n = 5 by going
# 0, 1, 1, 2, 3, 5.
#
# Example 2:
#   Input: `n = 1`
#   Output: 1
#
# Example:
#   Input: `n = 10`
#   Output: 55
#

``` {r}
# Define a function to calculate the nth term of the Fibonacci series using recursion
fibonacci <- function(n) {
    if (n <= 1) {  
      # Base case: If n is 0 or 1, return n
      return(n)
    } else {
        # Recursive case: Calculate the nth term using recursion
        return(fibonacci(n - 1) + fibonacci(n - 2))
    }
}


fibonacci(1)
fibonacci(2)
fibonacci(5)
fibonacci(10)


#Index of 1 solution
fibonacci <- function(n) {
  if (n == 1) {
    return(0)
  } else if (n == 2) {
    return(1)
  } else {
    return(fibonacci(n - 1) + fibonacci(n - 2))
  }
}


```




# Write a R program that calculates the factorial of a given number.
# Hint 1: While loop
``` {r}
# Function to calculate the factorial of a given number
calculate_factorial <- function(n) {
    # Initialize variables
    fact <- 1
    i <- 1
    
    # Check if the entered number is negative
    if (n < 0) {
        print("Factorial is not defined for negative numbers.")
    } else if (n == 0) { # Check if the entered number is 0
        print("Factorial of 0 is 1.")
    } else { # Calculate factorial using a while loop
        while (i <= n) {
            fact <- fact * i
            i <- i + 1
        }
        # Return the factorial of the entered number
        return(fact)
    }
}

factorial_result <- calculate_factorial(5)
```

# Write a R program function to check if a given number is a palindrome.
# Hint 1: Recursion
 
``` {r}
# Define a function to check if a given number is a palindrome using recursion
is_palindrome <- function(number) {
    # Convert the number to a character string
    num_str <- as.character(number)
    
    # Define a helper function to check if a string is a palindrome
    is_palindrome_helper <- function(str) {
        if (nchar(str) <= 1) {
            return(TRUE)  # Base case: Single character or empty string is a palindrome
        } else {
            first_char <- substr(str, 1, 1)  # Get the first character
            last_char <- substr(str, nchar(str), nchar(str))  # Get the last character
            
            # Check if the first and last characters are equal
            if (first_char != last_char) {
                return(FALSE)  # If not equal, not a palindrome
            } else {
                # Recursively check the substring without the first and last characters
                return(is_palindrome_helper(substr(str, 2, nchar(str) - 1)))
            }
        }
    }
    
    # Call the helper function with the number converted to a string
    return(is_palindrome_helper(num_str))
}
is_palindrome(42324)
is_palindrome(1234)
```

#Give me the primes:
Prime numbers include 2, 3, 5, 7, and any other number that’s only divisible by itself and 1. Write a function in R that takes an integer as a parameter and returns all the prime numbers up to and including that integer.

``` {r}

```